Charity analysis

### 2022-07-18 Shiny/Test/Flexdashboard rows.Rmd
Removing DT package as it's not used. Commenting.

```{r setup, include=FALSE}
# Packages using pacman
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
       flexdashboard, MetBrewer, DT, fontawesome, htmltools)
# Using package fontawesome for fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

#---- Plots --------------------------------------------------------------------    
    # creating plots

@@

    # Creating fancier plot
    fancyplot <- reactive(
      htmldata() |> 
        select(
          year, lederlonn, leder_annen_godtgjorelse
         ) |> 
        rename(
          Year = year,
          Salary = lederlonn,
          `Other compensation` = leder_annen_godtgjorelse
        ) |> 
        pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
        ggplot(aes(Year, value, fill = Compensation)) +
        geom_col() +
        scale_y_continuous(
        labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
                    label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
                    label_dollar(prefix = "? "))
         ) +
        scale_fill_met_d("Troy") +
        labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
        subtitle = ifelse(length(unique(htmldata()$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
        )

  # Creating fancy plotlyplot
    fancyplotly <- reactive({
      ggplotly(fancyplot())
    })
  # Creating fancy plotly output  
    output$fancyplotly <- renderPlotly(
      fancyplotly()
    )
})

>>>>

```{r setup, include=FALSE}
# Packages using pacman
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
       flexdashboard, MetBrewer, fontawesome, htmltools)
# Using package fontawesome for fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())
```

@@

#---- Plots --------------------------------------------------------------------    
    # creating plots - CEO compensation

@@

    # fancier plot function
    fancyplot <- reactive(
      htmldata() |> 
        select(
          year, lederlonn, leder_annen_godtgjorelse
         ) |> 
        rename( # renaming for the purposes of the plot
          Year = year,
          Salary = lederlonn,
          `Other compensation` = leder_annen_godtgjorelse
        ) |> 
        # pivoting to join the two values to use fill
        pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
        ggplot(aes(Year, value, fill = Compensation)) +
        geom_col() +
        scale_y_continuous(
          # Checking for uniform currency code
        labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
         ) +
        scale_fill_met_d("Troy") + # pretty colours
        labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(htmldata()$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
        )

  # Creating fancy plotlyplot
    fancyplotly <- reactive({
      ggplotly(fancyplot())
    })

  # Creating fancy plotly output  
    output$fancyplotly <- renderPlotly(
      fancyplotly()
    )
})
